\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-02-10 paper.tex
fix informed sampling definition

Define the dynamics of a robot as 
\begin{equation}
\label{eq:kinematics}
\dot{x}(t) = f( x(t) , u(t) ), 
\end{equation}
in which $ x \in \calX \subseteq \mathbb{R}^n $ is the state of the robot, and $ u \in \calU \subseteq \mathbb{R}^m $ is the control input.
The dynamics determines how a state trajectory $ \gamma $ is like given duration $ T $, state $ x(t) $ and input $ u(t) $.
The cost of a trajectory $ \gamma $ is defined as the accumulated cost $ c( x(t), u(t) ) $ along the path, which is 
\begin{equation}
\label{eq:path_cost}
c(\gamma) = \int_0^{T} c( x(t), u(t) ) dt.
\end{equation}
Consider the obstacles in a workspace, we have $ \Cfree \subseteq \calX $.
Consider the bounds of the control input, we have $ \Ufree \subseteq \calU $.
The dynamics of the robot in Equation~\eqref{eq:kinematics}, free state space $  \Cfree $ and free control input space $ \Ufree $ determines a free trajectory space $ \Pi_{free} $, which contains all feasible trajectories $ \gamma \in \Gamma_{\rm free} $.
An optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost $ \pi^* = \min_{ \pi \in \Gamma_{free} } c( \gamma ) $ subject to constraints $ x(t) \in \Cfree  $ and $ u(t) \in \Ufree $.

>>>>

Define the dynamics of a robot as 
\begin{equation}
\label{eq:kinematics}
\dot{x}(t) = f( x(t) , u(t) ), 
\end{equation}
in which $ x \in \calX \subseteq \mathbb{R}^n $ is the state of the robot, and $ u \in \calU \subseteq \mathbb{R}^m $ is the control input.
The dynamics determines how a state trajectory $ \gamma $ is like given duration $ T $, state $ x(t) $ and input $ u(t) $.
There exists a free trajectory space $ \Pi_{free} $ that contains all feasible trajectories $ \gamma \in \Gamma_{\rm free} $.
It is determined by the system dynamics,$ \Cfree $ and $ \Ufree $, in which $ \Cfree \subseteq \calX $ is a free state space considering the obstacles in a workspace, and $ \Ufree \subseteq \calU $ is a free control space considering the bounds of control input. 
The cost of a trajectory $ \gamma $ is defined as the accumulated cost $ c( x(t), u(t) ) $ along the path, which is 
\begin{equation}
\label{eq:path_cost}
c(\gamma) = \int_0^{T} c( x(t), u(t) ) dt.
\end{equation}
An optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost $ \pi^* = \min_{ \pi \in \Gamma_{free} } c( \gamma ) $.
